On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
fig move

\begin{figure}[t!]
\begin{center}
\includegraphics[width=.24 \linewidth]{figs/basis.png}
% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
\caption{\textbf{Learning a dictionary from increasingly noisy data}. The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above. Three increasingly imprecise dictionaries (columns relabelled to best match original) are recovered by FastICA \cite{hyvarinen2000independent} with data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise increasing from left to right.}
\vspace{-.6 cm}
\label{noisyrecovery}
\end{center}
\end{figure}

@@

@@

We close with some remaining open challenges.  First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.  Additionally, given the NP-hardness of verifying the spark condition for matrices, is approximating a solution to Prob.~\ref{InverseProblem} or \ref{OptimizationProblem} also computationally hard?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}? In what special cases is it efficient to check that a solution to the problems is optimal? % [*** Incorporate this open problem with more words ***]

>>>>

@@

\begin{figure}
\begin{center}
\includegraphics[width=.24 \linewidth]{figs/basis.png}
% \includegraphics[width=.25 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_2042}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise0_4083.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise1_0205.png}
\includegraphics[width=.24 \linewidth]{figs/Ahat_FastICA_M640_K8_noise2_0409.png}
\caption{\textbf{Learning a dictionary from increasingly noisy data}. The (unraveled) basis elements of the $8 \times 8$ discrete cosine transform (DCT) form the 64 columns of the left-most matrix above. Three increasingly imprecise dictionaries (columns relabelled to best match original) are recovered by FastICA \cite{hyvarinen2000independent} trained on data generated from $8$-sparse linear combinations of DCT elements corrupted with additive noise (increasing from left to right).}
\vspace{-.6 cm}
\label{noisyrecovery}
\end{center}
\end{figure}

@@

We close with some remaining open challenges.  First, there is the basic problem of proving optimal lower bounds on sufficient sample size for uniqueness and stability in sparse coding.  Additionally, given the NP-hardness of verifying the spark condition for matrices, are the corresponding approximation Probs.~\ref{InverseProblem} and \ref{OptimizationProblem} also computationally hard?  In what special cases is it efficient to check that a solution is stably unique for these problems?  Finally, as $\ell_1$ relaxations for inferring sparse vectors have, in many cases \cite{eldar2012compressed}, the same solutions as for $\ell_0$, is there an $\ell_1$ version of Thm.~\ref{SLCopt}?  % [*** Incorporate this open problem with more words ***]
